\huge Tor's Usability for Censorship Circumvention

### 2016-04-15 pets2017-paper/pets2017-paper.tex
Fix extra space before a cite.

\section{Related Work} 
There have been three published user studies on Tor. Clark et. al examined various deployment
options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and Foxyproxy, and found that none of them 
were satisfactory from a usability perspective~\cite{clark2007usability}. Fabian et. al show that Tor's added latency 
~\cite{dingledine2009performance} causes users
to be frustrated, cancel requests more often, and prevents user adoption~\cite{fabian2010privately}. 
Norcie et. al found found that 
64\% of users are unable to continue with installation or browsing at least once due to difficulties~\cite{norcie2012eliminating}.

@@

\begin{itemize}
\item {\bfseries Tell people what to do.} Since a majority of the users will succeed if they click connect on the first screen, replacing the information about choices with explicit instructions to connect can lessen their cognitive load during the configuration process. 
\item{\bfseries Hide infrequently used options.} Hide the proxy screen and do not the option to configure a proxy unless it has been detected as necessary.
\item{\bfseries Tailor for at-risk users.} Currently, the interface is for the average user. We guide at-risk users to the correct configuration, but suggesting that they try the default first. However, this isn't ideal. 
\end{itemize}

@@

\begin{itemize}
\item{\bfseries Automate the configuration.} This sounds like a radical idea, but this wouldn't harm users today. Additionally, our study finds that most users would leak that they are using Tor when trying to circumvent an advanced censor. 
\item {\bfseries Automate after failure.} After an unsuccessful connection attempt, the user has already indicated that they are connecting to Tor on the network. Assuming that the significant difference is between being logged trying to connect to Tor or not at all, we can automate the entire configuration process thereafter without increasing risk. This may save our users a lot of headache. 
\item{\bfseries Ask about the risk.} Ask the users if they would be at risk if the process was automated, and automate the configuration process for all who are not at risk. The ones at risk will configure manually. The complication with this approach is that users may not be qualified to answer this question or may not trust Tor to answer honestly. 
\item{\bfseries Ask if users if they know what to do.} We ask users if they know how to configure a bridge and proxy, and automate the configuration process if they do not. However, there are ethical implications of making mistakes on behalf of the users if there is risk involved. 
\end{itemize}

@@

Thought that they needed a proxy: 
\begin{enumerate}
\item E2-OLD-X10-20160328-132828
\item E3-NEW-X18-20160330-170145
\item E3-NEW-X17-20160328-160037
\item E3-OLD-X06-20160325-175101
\item E3-OLD-X06-20160330-181926
\item E3-OLD-X24-20160328-155926
\end{enumerate}

Only tried connecting directly: 
\begin{enumerate}
\item E2-NEW-X21-20160323-133257 
\item E2-OLD-X04-20160330-181928
\item E2-OLD-X10-20160331-153028
\item E3-NEW-X05-20160324-132535
\item E3-NEW-X17-20160323-133002
\item E3-OLD-X06-20160328-132053
\item E3-OLD-X06-20160330-161525 
\item E3-OLD-X12-20160330-182011
\end{enumerate}

Didn't know what to do after connecting directly and default bridge: 
\begin{enumerate}
\item E3-NEW-X11-20160330-161511
\item E3-NEW-X11-20160331-174655
\item E3-NEW-X23-20160323-133346
\item E3-OLD-X06-20160331-174650
\item E3-OLD-X12-20160331-153055
\item E3-OLD-X30-20160328-134412
\end{enumerate}

Failed to use the bridges@torproject.org autoresponder: 
\begin{enumerate}
\item E3-NEW-X23-20160328-155924 (Figure \ref{autoresponder1})
\item E3-OLD-X12-20160325-140813 (Figure \ref{autoresponder2})
\item E3-OLD-X24-20160328-133857 (Figure \ref{autoresponder3})
\end{enumerate}

@@

Participants that downloaded Tor: 
\begin{enumerate}
\item E1-OLD-X32-20160328-134531(Figure \ref{mirror})
\item E2-NEW-X21-20160323-133257 (Figure \ref{techspot})
\item E2-OLD-X10-20160323-132505 (Figure \ref{downloadio})
\item E2-OLD-X28-20160328-134111 (Figure \ref{driverupdate})
\item E3-NEW-X11-20160330-161511 (Figure \ref{softsonic})
\end{enumerate}

>>>>

\section{Related Work} 
There have been three published user studies on Tor. Clark et. al examined various deployment
options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and Foxyproxy, and found that none of them 
were satisfactory from a usability perspective~\cite{clark2007usability}. Fabian et. al show that Tor's added
latency~\cite{dingledine2009performance} causes users
to be frustrated, cancel requests more often, and prevents user adoption~\cite{fabian2010privately}. 
Norcie et. al found found that 
64\% of users are unable to continue with installation or browsing at least once due to difficulties~\cite{norcie2012eliminating}.

@@

\begin{description}
\item {\bfseries Tell people what to do.} Since a majority of the users will succeed if they click connect on the first screen, replacing the information about choices with explicit instructions to connect can lessen their cognitive load during the configuration process. 
\item{\bfseries Hide infrequently used options.} Hide the proxy screen and do not the option to configure a proxy unless it has been detected as necessary.
\item{\bfseries Tailor for at-risk users.} Currently, the interface is for the average user. We guide at-risk users to the correct configuration, but suggesting that they try the default first. However, this isn't ideal. 
\end{description}

@@

\begin{description}
\item{\bfseries Automate the configuration.} This sounds like a radical idea, but this wouldn't harm users today. Additionally, our study finds that most users would leak that they are using Tor when trying to circumvent an advanced censor. 
\item {\bfseries Automate after failure.} After an unsuccessful connection attempt, the user has already indicated that they are connecting to Tor on the network. Assuming that the significant difference is between being logged trying to connect to Tor or not at all, we can automate the entire configuration process thereafter without increasing risk. This may save our users a lot of headache. 
\item{\bfseries Ask about the risk.} Ask the users if they would be at risk if the process was automated, and automate the configuration process for all who are not at risk. The ones at risk will configure manually. The complication with this approach is that users may not be qualified to answer this question or may not trust Tor to answer honestly. 
\item{\bfseries Ask if users if they know what to do.} We ask users if they know how to configure a bridge and proxy, and automate the configuration process if they do not. However, there are ethical implications of making mistakes on behalf of the users if there is risk involved. 
\end{description}

@@

{\bfseries Cause 1}: only tried connecting directly (8/23): 
\begin{itemize}
\item E2-NEW-X21-20160323-133257 
\item E2-OLD-X04-20160330-181928
\item E2-OLD-X10-20160331-153028
\item E3-NEW-X05-20160324-132535
\item E3-NEW-X17-20160323-133002
\item E3-OLD-X06-20160328-132053
\item E3-OLD-X06-20160330-161525 
\item E3-OLD-X12-20160330-182011
\end{itemize}

{\bfseries Cause 2}: didn't know what to do after connecting directly and default bridge (6/23): 
\begin{itemize}
\item E3-NEW-X11-20160330-161511
\item E3-NEW-X11-20160331-174655
\item E3-NEW-X23-20160323-133346
\item E3-OLD-X06-20160331-174650
\item E3-OLD-X12-20160331-153055
\item E3-OLD-X30-20160328-134412
\end{itemize}

{\bfseries Cause 3}: Thought that they needed a proxy (6/23): 
\begin{itemize}
\item E2-OLD-X10-20160328-132828
\item E3-NEW-X18-20160330-170145
\item E3-NEW-X17-20160328-160037
\item E3-OLD-X06-20160325-175101
\item E3-OLD-X06-20160330-181926
\item E3-OLD-X24-20160328-155926
\end{itemize}

{\bfseries Cause 4}: used the bridges autoresponder incorrectly (3/23): 
\begin{itemize}
\item E3-NEW-X23-20160328-155924 (Figure \ref{autoresponder1})
\item E3-OLD-X12-20160325-140813 (Figure \ref{autoresponder2})
\item E3-OLD-X24-20160328-133857 (Figure \ref{autoresponder3})
\end{itemize}

@@

Participants that downloaded Tor (5/124): 
\begin{itemize}
\item E1-OLD-X32-20160328-134531(Figure \ref{mirror})
\item E2-NEW-X21-20160323-133257 (Figure \ref{techspot})
\item E2-OLD-X10-20160323-132505 (Figure \ref{downloadio})
\item E2-OLD-X28-20160328-134111 (Figure \ref{driverupdate})
\item E3-NEW-X11-20160330-161511 (Figure \ref{softsonic})
\end{itemize}

Sources of downloads: 
\begin{itemize}
\item {\bfseries techspot.com -> 1download.io}: the ad firefox yahoo ad result for ``tor browser downloads.'' 
\item {\bfseries driverupdate.net}: the 5th chrome google search result for ``tor browser download.'' 
\item {\bfseries www.torservers.net/mirrors}: the first chrome google search result for ``tor browser mirror.''
\item {\bfseries techspot.com}: the 5th chrome google search result for ``tor browser download.''
\item {\bfseries softsonic.com}: the 2nd firefox yahoo search result for ``tor browser.''
\end{itemize}
